### 2019-01-30 README.Rmd
update ink to overview figure

* **The performance of methods** used for the [results overview figure](`r dynbenchmark::link_to_results("scripts/08-summary/overview.pdf")`) and the [dynguidelines](https://www.github.com/dynverse/dynguidelines) app. _Not yet available_, but can be accessed in the results folder.

>>>>

* **The performance of methods** used for the [results overview figure](`r dynbenchmark::link_to_results("scripts/08-summary/results_suppfig.pdf")`) and the [dynguidelines](http://guidelines.dynverse.org) app.
